Coherent optical association of a single molecule

### 2020-10-20 paper.tex
Mention molecular scattering scaling and mention longest lifetime measurement

These results suggest that the decoherence or loss we observed during the Raman transition
comes from either a higher than expected background scattering rate
or a different intrinsic or technical source that we have not accounted for.
We have observed a significant decrease in the coherence time without the ASE filter,
suggesting the spectral purity of the laser is a significant source of scattering.
Another source of decoherence could result from fluctuations in the power ratio
between the two beams resulting in a fluctuation in the resonance position.
In the experiment, we only stabilize the total power of the tweezer.

>>>>

\todo{change scattering to decoherence? since the fluctuation of light shift
  does not lead to scattering but only decherence.}
These results suggest that the decoherence or loss we observed during the Raman transition
comes from either a higher than expected background scattering rate
or a different intrinsic or technical source that we have not accounted for.
We have observed a significant decrease in the coherence time without the ASE filter,
suggesting the spectral purity of the laser is a significant source of scattering.
Another source of decoherence could result from fluctuations in the power ratio
between the two beams resulting in a fluctuation in the resonance position.
In the experiment, we only stabilize the total power of the tweezer.

In additional to calibrating the $\Omega_m$ and $\Omega_a$,
the scattering rate of the molecule is also depend on the tweezer power and detuning.
At $3\mathrm{mW}$ tweezer power, we have observed molecule lifetime as long as $1\mathrm{ms}$.
However, since the technical noise that can lead to decoherence
is not fully characterized in our experiment,
we are unable to further identify the source of the discrepancy based on this dependency.
